---
title: "SD_datavis"
author: "Daina Bouquin"
date: "October 23, 2015"
output: html_document
---
Additional exploritory analysis

```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

It could be interesting to do a comparitive analysis to that done on the Oscars data. For the data regarding the SanDiego awards, is there a visible relationship between winning best editing and winning any of the other awards like best picture?

```{r}
sdtable$year <- as.factor(sdtable$year)
sdtable$movie <- as.factor(sdtable$movie)

#Create column based on whether or not best_editing won
b <- ggplot(sdtable, aes(x=best_editing)) + geom_histogram(binwidth=2,colour="white")
c <- b + facet_grid(. ~ best_film)
d <- c + ggtitle("Winning Best Film\n As it Relates to Winning Best Editing")
d
```
Other potentially interesting analyses?

Best actress or best actor correlated more closely with most wins?
First we pull out a subset from the data where the film won either best actor or best actress
```{r}
sdtable$year <- as.factor(sdtable$year)
sdtable$movie <- as.factor(sdtable$movie)

# Extract all records where movie won best actor or actress
w_actorORactress <- filter(sdtable, best_actor == 1 | best_actress == 1)
nrow(w_actorORactress)
```
We have 37 films now that have won either best actor or best actress

We filter further to see if any films won both awards
```{r}
w_actorANDactress <- filter(sdtable, best_actor == 1 & best_actress == 1)
nrow(w_actorANDactress)
w_actorANDactress$movie
```
Only American Beauty has won both. In order to simplify this question, we remove this record so we do not create any confounds.
```{r}
w_actorORactress <- subset(w_actorORactress, movie!="American Beauty")
nrow(w_actorORactress)
```
Now that we've had a little look at the data, we'll reshape the data and create a column in the dataset to indicate the status of the various awards to see how those awards (particularly the gender-based ones) are related to other awards associated with the movies.

```{r}
tidy_awards <- w_actorORactress %>%
  gather(award, award_status, -movie, -year, best_film, best_cinematography, best_director, best_editing)

winners <- filter(tidy_awards, award_status == 1)

#not what I want but getting closer
# Want to facet other awards by whether or not the film best actor or actress
a <- ggplot(winners, aes(x=award_status)) + geom_histogram(binwidth=2,colour="white")
a + facet_grid(. ~ award)
```

